\section{Assumptions}
During the design of the project, several assumptions were made, they are listed here.
\begin{itemize}
\item Petrol card
\begin{itemize}
	\item A car owner can only have one petrol card.
	\item The petrol card is tamper-resistant, therefore provide integrity and confidentiality of their data and functionality.
	\item The balance on the petrol card can only be changed by an authenticated charging terminal
	\item Key material cannot be copied off the petrol card
\end{itemize}

\item Personalization
\begin{itemize}
\item Employees have been properly instructed and are trustworthy to not steal key material during the personalization of the petrol cards.
\item Employees who created the back-end did not have malicious intentions, such as building a backdoor.
\item Personalization terminals will have a reliable clock.
\item Key material cannot be copied off the personalisation terminal
\end{itemize}

\item Charging
\begin{itemize}
\item Charging terminals come pre-installed, or are installed by a trusted company
\item Charging terminal will have a reliable clock.
\item Key material cannot be copied off the charging terminal
\end{itemize}

\item Pumping
\begin{itemize}
\item Pumping terminals come pre-installed, or are installed by a trusted company
\item The pump is trusted to always communicate the right amount of fuel that has been released to the pumping terminal.
\item Pumping terminal will have a reliable clock.
\item Key material cannot be copied off the pumping terminal
\item The pumping terminal is able to store logs of transactions without compromising the integrity or confidentiality of the logs
\end{itemize}

\item Back-end
\begin{itemize}
\item The key material of the CA cannot be copied
\item The revocation list maintained by the back end cannot be altered in such a way that already revoked petrol cards or terminal will be removed by the revocation list. 
\end{itemize}
\end{itemize}

 
